\documentclass[a4paper]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Packages using
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\ifx\pdfoutput\undefined
	\usepackage[dvips]{graphicx}
	\DeclareGraphicsExtensions{.eps}
\else
	\usepackage[pdftex]{graphicx}
	\DeclareGraphicsExtensions{.pdf,.jpg,.png,.mps}
\pdfcompresslevel=9
\fi
\usepackage[bookmarks=true,bookmarksnumbered=true,hypertexnames=true,breaklinks=true,colorlinks=true]{hyperref}
\usepackage{amsmath,amssymb}
\usepackage[ansinew]{inputenc}
\usepackage[english]{babel}
\usepackage{indentfirst}
\addtolength{\topmargin}{-20mm}
\addtolength{\textheight}{10mm}

\begin{document}               % Begins the document

\title{Structure of XML Metadata}
\author{EagleUnit \\ (I-Chieh, Chinweze, Henry, Ray, Jones, Piyarul)} 
%\date{2010-10-10}             % If you want to set the date yourself.

\maketitle                     % Generates the title




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Team:
% EagleUnit
% Members: 
%  I-Chei, Chinweze, Jones, Ray, Hunry, Piyarul, Tim
% Relative files:
% 
% Note:    
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{XML metadata structure}
\subsection{ABSTRACT}
\label{sec:abs}
Our responsibility is to build a metadata schema which contains all information in the PDF and program it in a XML structure. This article present an overview of standards for metadata related to our responsibility. We review a number of metadata schemas in use today, including MODS, METS, METS+MODS+PREMIS, MARC21, MARC XML, and show the overviews and the pros and cons of each schema. Finally, through the examination of characteristics of these metadata schemas, we try to rank them and to suggest the optimum standard for our work.
\subsection{INTRODUCTION}
Metadata is defined as “data about data” or alternatively “information about
information”. In practice, Metadata is the administrative data used in both
manual and computerized systems for the organization and management of
documents (Underwood 2003).\\

The metadata schemas can be classified in to three types (Dempsey and Heery, 1997):\\\\
• Simple formats: it includes relatively unstructured data, typically automatically extracted from resources and indexed for searching. The data has little explicit semantics and does not support searching by field, such as Lycos, Altavista, Yahoo.\\\\	
• Structured formats: it includes data which contains full enough description to allow a user to assess the potential utility or interest of a resource without having to retrieve it or connect to it. The data is structured and supports fielded searching, such as Dublin Core, IAFA templates, RFC 1807, SOIF, LDIF.\\\\
• Rich formats: it includes includes fuller descriptive formats which may be used for location and discovery, but also have a role in documenting objects or, very often, collections of objects, such as ICPSR, CIMI, EAD, TEI, MARC.\\

XML markup, is the idiom of choice for the encoding and exchange of structured data. The XML namespace facility provides structural capabilities that HTML lacks, making it easier to achieve the principles of modularity and extensibility. The XML Schema specification defines a schema language that allows for the specification of application profiles that will increase the prospects for interoperability. (Duval 2002). Our work is need to build a metadata schema in XML structure, so next section we will introduce the schemas which has been implemented in the XML as mentioned previously.
\subsection{BACKGROUND}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 1. Different standards of metadata
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{Different standards of metadata}
\label{sec:mets}
There's many different standards existing to describe the metadata in different fields and applications. We list 5 of them and give a brief introduction to each one.

\begin{enumerate}
	\item METS\\
	{\bf Introduction}\\
	Metadata Encoding and Transmission Standard (METS) similar to XML encoding format for storing the descriptive, administrative, structural and behavioral metadata needed to manage complex digital objects in open and standardized way.
	
	In 1990s, Making of America II (MOA2) project was proposed to share vision between national digital libraries which provides a means for the Digital Library Federation (DLF) to investigate, refine, and recommend metadata elements and encodings used to discover, display, and navigate digital archival objects. MOA2 DTD was created to test MOA2 project.
	
	However, MOA2 DTD was limited in several ways. It provided no flexibility in terms of the exact metadata elements to be used for descriptive, administrative and structural metadata. Also, limited in scope to support for text and still image materials and no attempt to support time-based media such as audio or video materials. To solve those problems led to the creation of METS.
	
	{\bf Adventage}
	\begin{enumerate}
		\item METS to facilitate the exchange and interoperability of digital library objects across digital library systems.
		\item Provide support a practical and flexible packaging mechanism for the long-term preservation of digital library objects.
		\item The METS standard can be considered one of many efforts to try to determine, for one particular community, how complex sets of data and metadata might best be encoded to support both information exchange and information longevity.
	\end{enumerate}	
	{\bf Disadventage}
	\begin{enumerate}
		\item METS has gone some distance towards achieving these design goals, it is not in itself a guarantee of interoperability.
		\item There are some obvious practical difficulties in using METS for the long-term preservation of digital objects.
	\end{enumerate}
	{\bf Conclusion}\\	
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\item MODS\\
	{\bf Introduction}\\
	Metadata Object and Description Schema (MODS) is a schema for a bibliographic element set that may be used for a variety of purposes, and particularly for library applications. It is a MARC-compatible XML schema for encoding descriptive data. \\
	The Library of Congress' Network Development and MARC Standards Office, with interested experts, developed the Metadata Object Description Schema (MODS) in 2002 for a bibliographic element set that may be used for a variety of purposes, and particularly for library applications. As an XML schema it is intended to be able to carry selected data from existing MARC 21 records as well as to enable the creation of original resource description records. It includes a subset of MARC fields and uses language-based tags rather than numeric ones, in some cases regrouping elements from the MARC 21 bibliographic format. As of May 2015 this schema is in its third version (version 3.6). MODS is expressed using the XML schema language of the World Wide Web Consortium. The standard is maintained by the MODS Editorial Committee with support from the Network Development and MARC Standards Office of the Library of Congress.\\
	MODS could potentially be used as follows :\\
	• as an SRU specified format\\
	• as an extension schema to METS\\
	• to represent metadata for harvesting\\
	• for original resource description in XML syntax\\
	• for representing a simplified MARC record in XML\\
	• for metadata in XML that may be packaged with an electronic resource\\
	Features of MODS :\\
	• The elements generally inherit the semantics of MARC\\
	• Some data has been repackaged; in some cases what is in several data elements in MARC may be brought together into one in MODS\\
	• MODS does not assume the use of any specific cataloging code\\
	• Several elements have an optional ID attribute to facilitate linking at the element level.\\
	{\bf Adventage}
	\begin{enumerate}
		\item The element set is richer than Dublin Core.
		\item The element set is more compatible with library data than ONIX.
		\item The schema is more end user oriented than the full MARCXML schema.
		\item The element set is simpler than the full MARC format.
	\end{enumerate}	
	{\bf Disadventage}
	\begin{enumerate}
		\item An original MARC 21 record converted to MODS may not convert back to MARC 21 in its entirety without some loss of specificity in tagging or loss of data.
		\item In some cases if reconverted into MARC 21, the data may not be placed in exactly the same field that it started in because a MARC field may have been mapped to a more general one in MODS.
		\item MODS does not include business rules for populating the elements.
		\item Additional instructions would need to be provided for conversion details.
	\end{enumerate}
	{\bf Conclusion}\\
	MODS has a high level of compatibility with MARC records because it inherits the semantics of the equivalent data elements in the MARC 21 bibliographic format. It may be used for original resource description that allows for rich description that is generally compatible with existing library data and is expressed in XML syntax. Because it includes a subset of MARC fields and repackages some of them, it is particularly useful for technician input.\\
	An additional use of MODS is as an extension schema for descriptive matadata for METS object.
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\item METS+MODS+PREMIS\\
	{\bf Introduction}\\
	
	{\bf Adventage}
	\begin{enumerate}
		\item testA
		\item testB
	\end{enumerate}	
	{\bf Disadventage}
	\begin{enumerate}
		\item testA
		\item testB
	\end{enumerate}
	{\bf Conclusion}\\
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\item MARC 21\\
	{\bf Introduction}\\
	
	{\bf Adventage}
	\begin{enumerate}
		\item testA
		\item testB	
	\end{enumerate}	
	{\bf Disadventage}
	\begin{enumerate}
		\item testA
		\item testB
	\end{enumerate}
	{\bf Conclusion}\\
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%	
	\item MARCXML\\
	{\bf Introduction}\\
	To make up the less of internet compatibility of MARC 21, the Library of Congress developed an XML schema based on it. Which the schema is the MARCXML standard. The purpose of MARCXML is to build a metadata format with a simple, extensible and flexible structure, which can be presented in XML stylesheets. Since MARCXML was design to converged data from MARC 21, the structure and performance are very similar between these two standards.  \\
	{\bf Adventage}
	\begin{enumerate}
		\item Used in XML directly
		\item Easily work with MARC 21 system.
	\end{enumerate}	
	{\bf Disadventage}
	\begin{enumerate}
		\item The disadventage of MARC 21 can be almost totally found on MARCXML, except the ability of internet apllication.
	\end{enumerate}
	{\bf Conclusion}\\
	Since our responsibility is to construct an XML schema, MARCXML will be our choice if MARC 21 becomes the standard we work with.
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\item Dublin Core\\
	{\bf Introduction}\\
	Dublin Core's purpose is to provide a very simple set of metadata so   that people can describe Web-based information resources quickly and easily, even people with no formal training in that activity. It has fifteen core elements. These simple elements can be further defined to create more detailed metadata.\\
	The original Dublin Core Metadata Element Set consists of 15 metadata elements:\\
	1. Title 2. Creator 3. Subject 4. Description 5. Publisher 
	6. Contributor 7. Date 8. Type 9. Format 10. Identifier
	11. Source 12. Language 13. Relation 14. Coverage 15. Rights\\
	{\bf Adventage}
	\begin{enumerate}
		\item Encourage authors and publishers to provide Metadata in the type that can be automatically collected by resource discovery tools.
		\item Encourage web publishing tool that contains element of the Metadata module to be founded, which further simplify the creation of Metadata records.
		\item DC records can be the basis of more detailed cataloging records.
		\item After the DC becomes the standard, Metadata records can be understood by the user.
	\end{enumerate}	
	{\bf Disadventage}
	\begin{enumerate}
		\item There are no cataloging rules that determine how data will be entered in the fields. So although I wrote "creator = Karen Coyle", I could also have written "creator = Coyle, Karen." This allows people who are adopting Dublin Core to make use of whatever rules are common in their community, but it does mean that there is no consistency across different uses of Dublin Core.
		\item Does not work well for data conversion.
		\item Data values in non-mappable space will be left out, especially when a source schema has a richer structure than that of the target schema. E.g., from LOM records to DC records.
	\end{enumerate}
	{\bf Conclusion}\\
		One of the things that makes Dublin Core easy and usable by anyone is that there are no cataloging rules involved. This is something that goes against the article cataloging.
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	
	
\end{enumerate}





%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% The bibliography
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

	\bibliography{library}
	\clearpage 


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% figures
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage % Ends the current page and causes all figures and tables to be printed



\end{document}      % End of the document
