%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% To do list
% Year:
% 2017
% Team:
% RCPL, Rainy
% Members: 
% Dickson Lee(Rainy/2017), Rain Wu(Rainy/2017), Sareddy Reddy(Rainy/2017), 
% Lewis Hsu(RCPL/2017), Tam-Van Ngo(RCPL/2017), Paul Lin(RCPL/2017)
% [Format:Name(Team/Year)]
% Relative files:
% Main.tex, Future_work.tex
% Note:    
% Do not compile this file compile Main.tex to get the pdf file instead.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Future Work}
So far, we have implemented the full-text search function on our web page. 
After clicking the search icon, it can perform the full-text search through the PDF files in the database and extracts of the most similar parts. 
Besides, it can also display the title and its relevance in descending order on the result web page.

However, we did not perform the search function through a PDF reader.
Instead, we provide a search box on a web page which the user cannot click on a highlighted text and thereby perform a full-text search through the PDF reader. 
Therefore, it would be great to build or find a PDF reader which the strings inside the text can be clicked and perform full-text search through the PDF files in the database as the next step of the future work.
 
The current search process took quite a bit of time to a very small size of testing samples(89 articles), the response time of the system would be much more slower when the size of database increases. 
Therefore, optimization of a database, search function and the web server is needed. 
This will enhance the user experience while searching.
 
We also hope that more searching methods can be considered and implemented on the system. 
Apart from the performance of the web service, it is also worth providing a hyperlink to the original source of PDF file and using Harvard citation format.
Last but not least, visualization of the result is needed. The website should provide charts about the distribution of similarity score of different parts of the article to the search query, also provide service to show the desired result by selecting the relevant boxes(ex. rank by publishing year, show results based on different types of articles etc).